### 2019-04-11 thesis_proposal_LaTeX/Chapters/6_StateoftheArt.tex
min feature

>>>>

The flow curve results of Serie C are presented in Figure \ref{fig:SerieCflowCurve}. The sample with 1 $w t \%$ TBATFB concentration shows a shear thinning behaviour for shear rates varying between 0.1 to 15 $s^{-1}$. The 1 $w t \%$ sample describes a drop in viscosity for shear rates between 15 to 20 $s^{-1}$ followed by a stable state.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieCflowCurve.png}
\decoRule
\caption[Serie C - Flow curve]{Serie C - Flow curve}
\label{fig:SerieCflowCurve}
\end{figure}
